---
title: "FL Jump analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Detection

Same setup. We count the total number of jumps detected divided by 
number of jumps estimated (across 5000 distinct data vectors
of $n=200$ for the middle-jump case).
The black line is binary segmentation, green line is fused lasso.
The left is for 2-step algorithm, while the right is for 3-step algorithm.

```{r, echo = F}
rm(list=ls())
load("../experiments/experiment_jump_counter_2.RData")
true_jumps <- c(100,140)

# first a plot of detection
.grab_lines <- function(bs_res, fl_res, paramMat, k = 2){
  idx_vec <- which(paramMat[,"k"] == k)

  bs_line <- sapply(bs_res[idx_vec], function(x){
    sum(apply(x, 2, function(y){
      sum(sapply(true_jumps, function(true_jump){
        length(which(abs(y - true_jump) <= 2))
      }))
    }))/prod(dim(x))
  })

  fl_line <- sapply(fl_res[idx_vec], function(x){
    sum(apply(x, 2, function(y){
      sum(sapply(true_jumps, function(true_jump){
        length(which(abs(y - true_jump) <= 2))
      }))
    }))/prod(dim(x))
  })

  list(bs_line = bs_line, fl_line = fl_line)
}


par(mfrow = c(1,2))
tmp <- .grab_lines(bs_res, fl_res, paramMat, k = 2)
plot(NA, xaxt = "n", xlab='delta', ylab = "cond. powers", xlim = c(1,6),
     ylim = c(0,1), main = "Detection, 2-step algorithms")
axis(1, at=1:6, labels=paramMat[1:6,1])
lines(tmp$bs_line, col = 1, lwd = 2)
lines(tmp$fl_line, col = 3, lwd = 2)

tmp <- .grab_lines(bs_res, fl_res, paramMat, k = 3)
plot(NA, xaxt = "n", xlab='delta', ylab = "cond. powers", xlim = c(1,6),
     ylim = c(0,1), main = "Detection, 3-step algorithms")
axis(1, at=1:6, labels=paramMat[1:6,1])
lines(tmp$bs_line, col = 1, lwd = 2)
lines(tmp$fl_line, col = 3, lwd = 2)
```

## Number of jumps detected in the correct vincity

For delta = 2 or delta = 4, we also count the number of jumps in the correct
vincity.

This is for running the algorithms for 2 steps.
```{r, echo = F}
# next a detection numbers
.grab_mat <- function(bs_res, fl_res, paramMat, k = 2, SnR = 2){
  idx <- intersect(which(paramMat[,"k"] == k), which(paramMat[,"SnR"] == SnR))

  bs_vec <- table(apply(bs_res[[idx]], 2, function(x){
    sum(sapply(true_jumps, function(true_jump){
      length(which(abs(x - true_jump) <= 2))
    }))
  }))
  bs_vec <- bs_vec/sum(bs_vec)

  fl_vec <- table(apply(fl_res[[idx]], 2, function(x){
    sum(sapply(true_jumps, function(true_jump){
      length(which(abs(x - true_jump) <= 2))
    }))
  }))
  fl_vec <- fl_vec/sum(fl_vec)

  list(len.fl = fl_vec, len.bsfs = bs_vec)
}

.grab_mat(bs_res, fl_res, paramMat, k = 2, SnR = 2)
.grab_mat(bs_res, fl_res, paramMat, k = 2, SnR = 4)
```

This is for running the algorithms for 3 steps.
```{r, echo = F}
.grab_mat(bs_res, fl_res, paramMat, k = 3, SnR = 2)
.grab_mat(bs_res, fl_res, paramMat, k = 3, SnR = 4)
```

This is for running the algorithms for 4 steps.
```{r, echo = F}
.grab_mat(bs_res, fl_res, paramMat, k = 4, SnR = 2)
.grab_mat(bs_res, fl_res, paramMat, k = 4, SnR = 4)
```

## Simulation check
Finally, we demonstrate the same estimation setup to make sure I get
the same results as Justin.

```{r, echo = F}

load("../experiments/experiment_fl_check.RData")
middle_mutation <- function(lev, n){
  mn <- rep(0,n)
  mn[seq(from=n/2+1, to=n/2+round(.2*n))] <- lev
  mn
}

lev = 2
n = 200
mn = middle_mutation(lev=lev, n=n)
par(mfrow=c(2,3))
for(seed in 1:6){
  set.seed(seed)
  y = mn + rnorm(n)
  print(head(round(y,3)))
  plot(y, pch=16, col='grey50', main = paste0("seed=",seed))
  abline(v=res[[seed]][,1], col = (res[[seed]][,2]==+1)+1)
}
```

